Composition-climate paper

### 2015-07-29 Composition_Ecology.Rmd
Removed "Land use" values for cells without either PLS or FIA data to make the plotting look better.
The changes are largely around an issue in the main `Rmd` file.  It's not recognizing the `clim_changes` variable, for some reason, so I'm getting an eval error when I knit.
Not sure why.

Annual clim is modified so that tmean values are replaced by tdiff.

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: '`r format(Sys.time(), ''%d %B, %Y'')`'
output:
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
  word_document:
    fig_height: 6
    fig_width: 6
csl: ecology.csl
pandoc_args: -H margins.sty
bibliography: goringetal_references.bib
---

@@

```{r setup-knitr, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = " ",
  error = TRUE,
  eval = TRUE,
  cache = TRUE,
  tidy = TRUE

@@

@@

changes <- climate_values$modern$value - climate_values$past$value

@@

Methods
===============
We pair pre-settlement vegetation data from the Public Land Survey System aggregated to a 64km^2^ grid [@goring2015preset] with annually resolved climate data for the region.  PLSS vegetation data contains no reported uncertainty, however it is spatially discontinuous, particularly in the south where digitization of PLSS records has occured at a slower rate.  Additionally, data in the northeastern United States [@thompson2013four] from town Proprietor Surveys is recorded arially, with no variance within township polygons.  To accomodate these different data sources a conditional autoregressive model was applied to the data, providing the ability to obtain uncertainty estimates across the domain [@paciorek2015comp].

@@

Mean temperatures in the region show an average increase of `r round(changes[3], 2)`^o^C since the 1895-1925 normal.  Annual precipitation has increased slightly (`r round(changes[1], 0)`mm), and maximum annual temeprature has declined slightly (`r round(changes[2], 2)`^o^C)).  The most significant change has been in annual minimum temperatures, which have increased by `r round(changes[4], 1)` since the 1895-1925 normal.  This broad scale increase in winter temperatures is widely accepted, and results in an overall shift in the winter 'climate space' for the region.

>>>>

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
  word_document:
    fig_height: 6
    fig_width: 6
csl: ecology.csl
pandoc_args: -H margins.sty
bibliography: goringetal_references.bib
---

@@

```{r setup-knitr, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = " ",
  error = TRUE,
  eval = TRUE,
  cache = FALSE,
  tidy = TRUE

@@

land_use <- land_use[land_use$cell %in% c(pls_data$cell, agg_dens$cell),]

@@

@@

Methods
===============
We pair pre-settlement vegetation data from the Public Land Survey System aggregated to a 64km^2^ grid [@goring2015preset] with annually resolved climate data for the region.

@@

`r clim_change <- climate_values$modern$value - climate_values$past$value `

Mean temperatures in the region show an average increase of `r round(clim_change[3], 2)`^o^C since the 1895-1925 normal.  Annual precipitation has increased slightly (`r round(clim_change[1], 0)`mm), and maximum annual temeprature has declined slightly (`r round(clim_change[2], 2)`^o^C)).  The most significant change has been in annual minimum temperatures, which have increased by `r round(clim_change[4], 1)` since the 1895-1925 normal.  This broad scale increase in winter temperatures is widely accepted, and results in an overall shift in the winter 'climate space' for the region.
